MODELLING THE CO-EVOLUTION OF TRADE AND CULTURE IN PAST SOCIETIES

### 2015-07-20 article.tex
revision etape 3 all bio miss Bigger Legend

\section*{AUTHOR BIOGRAPHIES}
\noindent {\bf SIMON CARRIGNON} is a PhD student at the Pompeu Fabra University. He holds a M.S. in in Cognitive Sciences and a M.A. in History and Philosophy of Science. His work focus on the use of computer modeling and evolutionary method to study Complex Systems. His email address is \email{simon.carrignon@bsc.es}.

\noindent {\bf JEAN-MARC MONTANIER} has obtained his engineering title in the domain of embedded computing. Since then, he has complete a Ph.D. in collective robotics at Universit\'e Paris-Sud XI. The topic of this Ph.D. was focused on the adaptation of a swarm of robots to unknown environments. His latest work in this area has addressed the learning of cooperative strategies, as well as the division of labour. He is now working in a new domain which proposes to apply Agent-Based Models to study economical and cultural evolution. His email address is \email{jeanmarc.montanier@bsc.es}.

\noindent {\bf XAVIER RUBIO-CAMPILLO}

>>>>

\section*{AUTHOR BIOGRAPHIES}
\noindent {\bf SIMON CARRIGNON} is a PhD student in Computer Applications in Science and Engineering, Barcelona Supercomputing Center. He holds a M.S. in Cognitive Sciences and a M.A. in History and Philosophy of Science. His works focused on the use of computer modeling and evolutionary method to study Complex Systems, ranging from Evolutionary Biology to Human and Cultural Dynamics. His email address is \email{simon.carrignon@bsc.es}.

\noindent {\bf JEAN-MARC MONTANIER} is Researcher in Computer Applications in Science and Engineering, Barcelona Supercomputing Center. He has obtained his engineering title in the domain of embedded computing and holds a Ph.D. in collective robotics. His topics of interest focused on Agent-Based Modeling, swarm adaptation, learning of cooperative strategies, division of labour and more recently study of economical and cultural evolution. His email address is \email{jean.montanier@bsc.es}.

\noindent {\bf XAVIER RUBIO-CAMPILLO} is Researcher in Computer Applications in Science and Engineering, Barcelona Supercomputing Center. He has a transdisciplinary training of Computer Science (BSc) and Humanities (PhD) with a strong emphasis on the study of past societies using historical and archaeological contexts. His main research line is the application of formal models to explore the processes of cultural evolution in past societies. His email address is \email{xavier.rubio@bsc.es}.
